Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-04-07 ms/SI.Rmd
clean

```{r caching, include=FALSE, eval=TRUE}
library(knitr)
library(tidyverse)
library(methods)
source("../scripts/rmd_func.R")
basename <- "LMA_method"
opts_chunk$set(fig.path = paste("figs/", sep=""))
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE,
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')

@@

val <- yaml::yaml.load_file("../values.yml")
```

@@

![](../figs/fig1.png){ width="600" style="display: block; margin: 0 auto" }

@@

![](../figs/LMAratio2.png){style="display: block; margin: 0 auto" }

@@

```{r, eval=TRUE, echo=FALSE}
tree <- read_csv("../data/tree_data.csv")

tree2 <- tree |>
  filter(!is.na(LMAdisc)) |>
  filter(!is.na(LMAleaf)) |>
  filter(!is.na(LTleaf)) |>
  rename(LT = LTleaf) |>
  rename(LA = LAleaf) |>
  mutate(Dry_mass_disc2 = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4 / 2,
   TRUE ~ LMAdisc * 0.889 * 10^-4 / 3
                )) |>
  mutate(Dry_mass_disc = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4,
   TRUE ~ LMAdisc * 0.889 * 10^-4
                )) |>
  mutate(PCH = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm"))

fit <- lm(log(Dry_mass_disc) ~ scale(log(LT)) + scale(log(LA)) + PCH, tree2)

s <- summary(fit)
tb <- s$coefficients |> round(3) |> signif(3)
colnames(tb) <- c("Estimate", "SE", "t-value", "*P* value")
tb[,4] <- ifelse(tb[,4] < 0.001, "< 0.001", tb[,4])
rownames(tb)[2] <- "log(Leaf thickness)"
rownames(tb)[3] <- "log(Leaf area)"
rownames(tb)[4] <- "Large leaf punch"

tb |>
  kable() |>
  kable_styling()
```

@@

![](../figs/LMA_sp_gr_both.png){ width="600" style="display: block; margin: 0 auto" }

@@

![](../figs/fig_cv2.png){ width="600" style="display: block; margin: 0 auto" }

>>>>

```{r caching, include=FALSE, eval=TRUE}
library(knitr)
library(tidyverse)
library(methods)
library(targets)
basename <- "LMA_method"
opts_chunk$set(fig.path = paste("figs/", sep = ""))
opts_chunk$set(tidy = FALSE,
               warning = FALSE,
               message = FALSE,
               comment = NA,
               verbose = TRUE,
               cache = FALSE,
               echo = FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')

@@

val <- yaml::yaml.load_file("values.yml")
```

@@

![](../figs/lma_ld.png){ width="600" style="display: block; margin: 0 auto" }

@@

![](../figs/ratio.png){style="display: block; margin: 0 auto" }

@@

```{r, eval=TRUE, echo=FALSE}
tar_load(dm_lm_tab)
dm_lm_tab |>
  kable(format = "html") |>
  kable_styling()
```

@@

![](../figs/lalt_sep_grid.png){ width="600" style="display: block; margin: 0 auto" }

@@

![](../figs/cv_sep.png){ width="600" style="display: block; margin: 0 auto" }
